[dcpo_gender_roles]: A Dataset of Dynamic Comparative Public Opinion Toward Egalitarian Gender Roles

### 2020-10-19 paper/dcpo_gender_roles.Rmd
adding lines

After examining all questionnaires asking opinions about gender roles from series of cross-national surveys including World Value Survey (WVS) and surveys conducted in individual countries or regions such as Arab Barometer, Korean General Social Survey, etc., we classify them into four categories: 1) egalitarian gender roles in the public sector which has been generally dominated by male, 2) those in private sector where the role of female has been emphasized, 3) the balance of female role in private and public sector, and 4) male dominance over women. 
Questionnaires related to the first dimension are asking respondents about the role of women or perspective on women in the public sector.
For example, "On the whole, men make better business executives than women do", "Would you say that most men are better suited emotionally for politics than are most women, that men and women are equally suited, or that women are better suited than men in this area?", "When jobs are scarce, men have more right to a job than women", "Some say that in general, men are better political leaders than women. Do you strongly agree, agree, disagree or strongly disagree?", and other similar questionnaires are classified as the first dimension.
Questionnaires about childcare or housework such as "A man can be responsible for looking after the home and children just as well while the woman works full-time" or "A father should be as heavily involved in the care of his children as the mother" are classified as the second dimension.

>>>>

After examining all questionnaires asking opinions about gender roles from series of cross-national surveys including World Value Survey (WVS) and surveys conducted in individual countries or regions such as Arab Barometer, Korean General Social Survey, etc., we classify them into four categories: 1) egalitarian gender roles in the public sector which has been generally dominated by male, 2) those in private sector where the role of female has been emphasized, 3) the balance of female role in private and public sector, and 4) male dominance over women. 
Questionnaires related to the first dimension are asking respondents about the role of women or perspective on women in the public sector.
For example, "On the whole, men make better business executives than women do", "Would you say that most men are better suited emotionally for politics than are most women, that men and women are equally suited, or that women are better suited than men in this area?", "When jobs are scarce, men have more right to a job than women", "Some say that in general, men are better political leaders than women. Do you strongly agree, agree, disagree or strongly disagree?", and other similar questionnaires are classified as the first dimension.
Questionnaires about childcare or housework such as "A man can be responsible for looking after the home and children just as well while the woman works full-time" or "A father should be as heavily involved in the care of his children as the mother" are classified as the second dimension.
The rest of questionnaires are classifed into the third or fourth dimensions. While questionnaires such as "A working mother can establish just as warm and secure a relationship with her children as a mother who does not work" and "A pre-school child is likely to suffer if his or her mother works" are about the third dimension, others including "View on Change of Surname at Marriage" and "A woman can travel abroad by herself if she wishes" are related to the fourth dimension.
